Palmer Archipelago Penguins Data in the palmerpenguins R Package - An Alternative to Anderson's \emph{Irises}

### 2020-08-05 penguins.Rmd
move over to R Journal formattng (#11)
* remove text (code only version)

* clean up repo, start populating .Rmd & bib

* update penguins paper

* Move to R Journal formatting, update figures

```{r, penguins-pairs, fig.cap = "Distribution and correlations for numeric variables in the penguins data (flipper length (mm), body mass, (g) bill length (mm) and bill depth (mm)) for the three observed species: gentoo (green, triangles); chinstrap (blue, circles); and Adélie (orange, squares). Correlations are Pearson's r (*p < 0.05; **p < 0.01; ***p < 0.001).", warning = FALSE, message = FALSE, echo = FALSE}
penguin_pairs <- penguins %>%
  mutate(species = as.character(species)) %>% 
  mutate(species = case_when(
    species == "Adelie" ~ "Adélie", 
    TRUE ~ species
  )) %>% 
  select(species, where(is.numeric)) %>% 
  ggpairs(aes(color = species, shape = species),
          columns = c("flipper_length_mm", "body_mass_g", 
                      "bill_length_mm", "bill_depth_mm"),
          columnLabels = c("Flipper length (mm)","Body mass (g)", "Bill length (mm)", "Bill depth (mm)"),
          upper = list(continuous = wrap("cor", size = 2.7, color = "black")),
          lower = list(continuous = wrap(ggally_points, size = 1.3))) +
  scale_fill_manual(values = c("#e59f00","#0072b2","#009e73")) +
  scale_color_manual(values = c("#e59f00","#0072b2","#009e73")) +
  scale_shape_manual(values = c(15,16,17)) +
  theme_minimal() +
  theme(
        text = element_text(size = 9),
        panel.grid.major = element_line(colour = NA),
        panel.grid.minor = element_blank(),
        panel.border = element_rect(color = "gray80", fill = NA)
        )

@@

There exist numerous opportunities to explore linear relationships and correlations in **penguins** and **iris** both within and across species (Figures \ref{fig:penguins-pairs} & \ref{fig:iris-pairs}). Here, we highlight one comparison that is uniquely similar: petal dimensions (petal length versus petal width) from iris, and penguin size (flipper length versus body mass) in penguins (Figure 3). The overall trend across all three species is approximately linear for both iris and penguins (Figure 3A,B). Teachers may encourage students to explore how simple linear regression results and predictions differ when the species variable is omitted (Figure 3A,B), compared to multiple linear regression with species included (Figure 3C,D).

@@

### Penguins bonus: Simpson’s Paradox

Simpson’s Paradox is a data phenomenon in which a trend observed between variables is reversed when data are pooled, omitting a meaningful variable. While often taught and discussed in statistics courses, finding a real-world and approachable example of Simpson’s paradox can be a challenge. Here, we show one (of several possible; see Figure XX) Simpson’s Paradox examples in **penguins**: exploring bill dimensions with and without *species* included (Figure XX). When penguin *species* is omitted (Figure XX), the bill length and depth appear negatively correlated overall. The trend is reversed when *species* is included, revealing a positive correlation between bill length and bill depth (Figure XX)

@@

A comparison of PCA with the four variables of structural size measurements in **penguins** and **iris** (both normalized prior to PCA) reveals highly similar results (Figure XX). For both datasets, one species is distinct (gentoo penguins, and setosa irises) while the other two species (chinstrap/Adélie and versicolor/virginica) appear somewhat overlapping in the first two principal components (Figure XX). Variance explained by each principal component (PC) is similar, particularly for PC1 and PC2: for **penguins**, 88.15% of total variance is captured by the first two PCs, compared to 95.81% for **iris**, with a similarly large percentage of variance captured by PC1 and PC2 in each (Figure XX).

@@

K-means clustering with penguin bill dimensions and iris petal dimensions yields largely distinct clusters each dominated by one species (Figure XX, Table XX). For iris petal dimensions, k-means yields a perfectly separated cluster (Cluster 1) containing all 50 setosa iris observations and zero misclassified virginica or versicolor irises (Table 4). While clustering is not perfectly distinct for any penguin species, each species is largely contained within a single cluster, with little overlap from the other two species. For example, considering Adélie penguins (orange observations in Figure 6A): 147 (out of 151) Adélie penguins are assigned to Cluster 1, zero are assigned to Cluster 2, and 4 are assigned to the chinstrap-dominated Cluster 3 (Table 4). Only 5 (of 68) chinstrap penguins and 1 (of 123) gentoo penguins are assigned to the Adélie-dominated Cluster 1 (Table 4).

>>>>

```{r, penguins-pairs, fig.cap = "Distribution and correlations for numeric variables in the penguins data (flipper length (mm), body mass, (g) bill length (mm) and bill depth (mm)) for the three observed species: gentoo (green, triangles); chinstrap (blue, circles); and Adélie (orange, squares). Correlations are Pearson's r (*p < 0.05; **p < 0.01; ***p < 0.001).", warning = FALSE, message = FALSE, echo = FALSE}
penguin_pairs <- penguins %>%
  mutate(species = as.character(species)) %>% 
  mutate(species = case_when(
    species == "Adelie" ~ "Adélie", 
    TRUE ~ species
  )) %>% 
  select(species, where(is.numeric)) %>% 
  ggpairs(aes(color = species, shape = species),
          columns = c("flipper_length_mm", "body_mass_g", 
                      "bill_length_mm", "bill_depth_mm"),
          columnLabels = c("Flipper length (mm)","Body mass (g)", "Bill length (mm)", "Bill depth (mm)"),
          upper = list(continuous = wrap("cor", size = 2.7)),
          lower = list(continuous = wrap(ggally_points, size = 1.3))) +
  scale_fill_manual(values = c("darkorange","#0072b2","#009e73")) +
  scale_color_manual(values = c("darkorange","#0072b2","#009e73")) +
  scale_shape_manual(values = c(15,16,17)) +
  theme_minimal() +
  theme(
        text = element_text(size = 9),
        panel.grid.major = element_line(colour = NA),
        panel.grid.minor = element_blank(),
        panel.border = element_rect(color = "gray80", fill = NA)
        )

@@

There exist numerous opportunities to explore linear relationships and correlations in **penguins** and **iris** both within and across species (Figures \ref{fig:penguins-pairs} & \ref{fig:iris-pairs}). Here, we highlight one comparison that is uniquely similar: petal dimensions (petal length versus petal width) from **iris**, and penguin size (flipper length versus body mass) in **penguins** (\ref{fig:linear-example}). The overall trend across all three species is approximately linear for both **iris** and **penguins**. Teachers may encourage students to explore how simple linear regression results and predictions differ when the species variable is omitted, compared to multiple linear regression with species included (\ref{fig:linear-example}).

```{r, linear-example, fig.cap = "Representative linear relationships for penguin flipper length (mm) and body mass (g) for Adélie (orange circles), chinstrap (blue triangles), and gentoo (green squares) penguins (A), and iris petal length (cm) and width (cm) for setosa (light gray circles), versicolor (dark gray triangles) and virginica (black squares) irises (B). Within-species linear model is visualized for each penguin or iris species.", echo = FALSE, out.width = '6in', fig.align='center', fig.pos='htbp'}

knitr::include_graphics('fig/linear_example.png')

@@

Simpson’s Paradox is a data phenomenon in which a trend observed between variables is reversed when data are pooled, omitting a meaningful variable. While often taught and discussed in statistics courses, finding a real-world and approachable example of Simpson’s paradox can be a challenge. Here, we show one (of several possible; see Figure \ref{fig:penguins-pairs}) Simpson’s Paradox examples in **penguins**: exploring bill dimensions with and without *species* included (Figure \ref{fig:simpsons}). When penguin *species* is omitted (Figure \ref{fig:simpsons} A), bill length and depth appear negatively correlated overall. The trend is reversed when *species* is included, revealing an obviously positive correlation between bill length and bill depth within species (Figure \ref{fig:simpsons} B).

```{r, simpsons, fig.cap = "Trends for penguin bill dimensions (bill length and bill depth, millimeters) if the ‘species’ variable is excluded (A) or included (B), illustrating Simpson’s Paradox. Note: linear regression for bill dimensions without including species in (A) is ill-advised; the linear trendline is only included to visualize trend reversal for Simpson’s Paradox when compared to (B).", echo = FALSE, out.width = '6in', fig.align='center', fig.pos='htbp'}

knitr::include_graphics('fig/simpson_gg.png')

@@

A comparison of PCA with the four variables of structural size measurements in **penguins** and **iris** (both normalized prior to PCA) reveals highly similar results (Figure \ref{fig:pca}). For both datasets, one species is distinct (gentoo penguins, and setosa irises) while the other two species (chinstrap/Adélie and versicolor/virginica) appear somewhat overlapping in the first two principal components (Figure \ref{fig:pca} A,B). Variance explained by each principal component (PC) is similar, particularly for PC1 and PC2: for **penguins**, 88.15% of total variance is captured by the first two PCs, compared to 95.81% for **iris**, with a similarly large percentage of variance captured by PC1 and PC2 in each (Figure \ref{fig:pca} C,D).

```{r, pca, fig.cap = "Principal component analysis biplots and scree plots for structural size measurements in penguins (A,C) and iris (B,D), revealing similarities in multivariate patterns, variable loadings, and variance explained by each component. For penguins, variables are flipper length (mm), body mass (g), bill length (mm) and bill depth (mm); groups are visualized by species (Adélie = orange circles, chinstrap = blue triangles, gentoo = green squares). For iris, variables are petal length (cm), petal width (cm), sepal length (cm) and sepal width (cm); groups are visualized by species (setosa = light gray circles, versicolor = dark gray triangles, virginica = black squares). Values above scree plot columns (C,D) indicate percent of total variance explained by each of the four principal components.", echo = FALSE, out.width = '6in', fig.align='center', fig.pos='htbp'}

knitr::include_graphics('fig/pca_plots.png')

@@

K-means clustering with penguin bill dimensions and iris petal dimensions yields largely distinct clusters each dominated by one species (\ref{fig:kmeans}). For iris petal dimensions, k-means yields a perfectly separated cluster (Cluster 1) containing all 50 setosa iris observations and zero misclassified virginica or versicolor irises (Table 2). While clustering is not perfectly distinct for any penguin species, each species is largely contained within a single cluster, with little overlap from the other two species. For example, considering Adélie penguins (orange observations in Figure \ref{fig:kmeans} A): 147 (out of 151) Adélie penguins are assigned to Cluster 1, zero are assigned to Cluster 2, and 4 are assigned to the chinstrap-dominated Cluster 3 (Table 2). Only 5 (of 68) chinstrap penguins and 1 (of 123) gentoo penguins are assigned to the Adélie-dominated Cluster 1 (Table 2).

```{r, include = FALSE, echo = FALSE}
# Including so kable table can be created here

# TWO VARIABLE k-means comparison
# Penguins: Bill length vs. bill depth
# Iris: petal length vs. petal width

pb_species <- penguins %>% 
  select(species, starts_with("bill")) %>% 
  drop_na()

pb_nospecies <- pb_species %>% 
  select(-species) %>% 
  recipe() %>% 
  step_normalize(all_numeric()) %>% 
  prep() %>% 
  juice()

# Perform k-means on penguin bill dimensions (k = 3, w/20 centroid starts)
# save augmented data
pb_clust <- 
  pb_nospecies %>% 
  kmeans(centers = 3, nstart = 20) %>% 
  broom::augment(pb_species)

# Plot clusters
pb_kmeans_gg <- 
  pb_clust %>% 
  ggplot(aes(x = bill_length_mm, y = bill_depth_mm)) +
  geom_text(aes(label = .cluster, color = species),
            key_glyph = draw_key_rect) +
  scale_color_manual(values = c("darkorange","#0072b2","#009e73"))+
  theme(legend.position = "bottom",
         panel.border = element_rect(fill = NA, color = "gray70"))

# Get counts in each cluster by species
pb_clust_n <- pb_clust %>% 
  count(species, .cluster) %>% 
  pivot_wider(names_from = species, values_from = n, names_sort = TRUE) %>% 
  arrange(.cluster)

### Iris k-means

ip_species <- iris %>% 
  select(Species, starts_with("Petal"))

# remove species factor & scale petal dimensions: 
ip_nospecies <- ip_species %>% 
  select(-Species) %>% 
  recipe() %>% 
  step_normalize(all_numeric()) %>% 
  prep() %>% 
  juice()

# Perform k-means on iris petal dimensions (k = 3, w/20 centroid starts)
ip_clust <- 
  ip_nospecies %>% 
  kmeans(centers = 3, nstart = 20) %>% 
  broom::augment(ip_species)

# Plot clusters
ip_kmeans_gg <- 
  ip_clust %>% 
  ggplot(aes(x = Petal.Length, y = Petal.Width)) +
  geom_text(aes(label = .cluster, color = Species), 
            key_glyph = draw_key_rect) +
  theme(legend.position = "bottom",
         panel.border = element_rect(fill = NA, color = "gray70")) +
  scale_color_manual(values = c("gray70","gray50","black"))

# Get counts in each cluster by species
ip_clust_n <- ip_clust %>% 
  count(Species, .cluster) %>% 
  pivot_wider(names_from = Species, values_from = n, names_sort = TRUE) %>% 
  arrange(.cluster)

# Combine kmeans plots for penguins & iris
(pb_kmeans_gg | ip_kmeans_gg) + plot_annotation(tag_levels = "A")

# ggsave(here("fig","kmeans.png"), width = 8, height = 4.5)

kmeans_2var_table <- cbind(pb_clust_n, ip_clust_n) %>% 
  kable(caption = "Grouped sample size for iris (by species; n = 150 total) and penguins (by species and sex; n = 344 total). Penguins can be further grouped by variables for island and study year.", align = "lclccc") %>% 
  kable_styling(full_width = FALSE) %>% 
  column_spec(c(5:8), background = "gainsboro") %>% 
  add_header_above(c("Penguins cluster assignments" = 4, "Iris cluster assignments" = 4))
```

```{r, kmeans, fig.cap = "K-means clustering outcomes for penguin bill dimensions (A) and iris petal dimensions (B). Numbers indicate the cluster to which an observation was assigned, revealing a high degree of separation between species for both penguins and iris.", echo = FALSE, out.width = '6in', fig.align='center', fig.pos='htbp'}

knitr::include_graphics('fig/kmeans.png')
```

```{r, echo = FALSE}
kmeans_2var_table <- cbind(pb_clust_n, ip_clust_n) %>% 
  kable(col.names = c("Cluster", "Adélie", "chinstrap", "gentoo", "Cluster", "setosa", "versicolor", "virginica"),
        caption = "K-means cluster assignments by species based on penguin bill length (mm) and depth (mm), and iris petal length (cm) and width (cm).", align = "cccccc") %>% 
  kable_styling(full_width = FALSE) %>% 
  add_header_above(c("Penguins cluster assignments" = 4, "Iris cluster assignments" = 4))

kmeans_2var_table
```

### 2020-08-05 penguins.tex
move over to R Journal formattng (#11)
* remove text (code only version)

* clean up repo, start populating .Rmd & bib

* update penguins paper

* Move to R Journal formatting, update figures

There exist numerous opportunities to explore linear relationships and
correlations in \textbf{penguins} and \textbf{iris} both within and
across species (Figures \ref{fig:penguins-pairs} \&
\ref{fig:iris-pairs}). Here, we highlight one comparison that is
uniquely similar: petal dimensions (petal length versus petal width)
from iris, and penguin size (flipper length versus body mass) in
penguins (Figure 3). The overall trend across all three species is
approximately linear for both iris and penguins (Figure 3A,B). Teachers
may encourage students to explore how simple linear regression results
and predictions differ when the species variable is omitted (Figure
3A,B), compared to multiple linear regression with species included
(Figure 3C,D).

@@

\hypertarget{penguins-bonus-simpsons-paradox}{%
\subsubsection{Penguins bonus: Simpson's
Paradox}\label{penguins-bonus-simpsons-paradox}}

Simpson's Paradox is a data phenomenon in which a trend observed between
variables is reversed when data are pooled, omitting a meaningful
variable. While often taught and discussed in statistics courses,
finding a real-world and approachable example of Simpson's paradox can
be a challenge. Here, we show one (of several possible; see Figure XX)
Simpson's Paradox examples in \textbf{penguins}: exploring bill
dimensions with and without \emph{species} included (Figure XX). When
penguin \emph{species} is omitted (Figure XX), the bill length and depth
appear negatively correlated overall. The trend is reversed when
\emph{species} is included, revealing a positive correlation between
bill length and bill depth (Figure XX)

@@

A comparison of PCA with the four variables of structural size
measurements in \textbf{penguins} and \textbf{iris} (both normalized
prior to PCA) reveals highly similar results (Figure XX). For both
datasets, one species is distinct (gentoo penguins, and setosa irises)
while the other two species (chinstrap/Adélie and versicolor/virginica)
appear somewhat overlapping in the first two principal components
(Figure XX). Variance explained by each principal component (PC) is
similar, particularly for PC1 and PC2: for \textbf{penguins}, 88.15\% of
total variance is captured by the first two PCs, compared to 95.81\% for
\textbf{iris}, with a similarly large percentage of variance captured by
PC1 and PC2 in each (Figure XX).

@@

K-means clustering with penguin bill dimensions and iris petal
dimensions yields largely distinct clusters each dominated by one
species (Figure XX, Table XX). For iris petal dimensions, k-means yields
a perfectly separated cluster (Cluster 1) containing all 50 setosa iris
observations and zero misclassified virginica or versicolor irises
(Table 4). While clustering is not perfectly distinct for any penguin
species, each species is largely contained within a single cluster, with
little overlap from the other two species. For example, considering
Adélie penguins (orange observations in Figure 6A): 147 (out of 151)
Adélie penguins are assigned to Cluster 1, zero are assigned to Cluster
2, and 4 are assigned to the chinstrap-dominated Cluster 3 (Table 4).
Only 5 (of 68) chinstrap penguins and 1 (of 123) gentoo penguins are
assigned to the Adélie-dominated Cluster 1 (Table 4).

>>>>

There exist numerous opportunities to explore linear relationships and
correlations in \textbf{penguins} and \textbf{iris} both within and
across species (Figures \ref{fig:penguins-pairs} \&
\ref{fig:iris-pairs}). Here, we highlight one comparison that is
uniquely similar: petal dimensions (petal length versus petal width)
from \textbf{iris}, and penguin size (flipper length versus body mass)
in \textbf{penguins} (\ref{fig:linear-example}). The overall trend
across all three species is approximately linear for both \textbf{iris}
and \textbf{penguins}. Teachers may encourage students to explore how
simple linear regression results and predictions differ when the species
variable is omitted, compared to multiple linear regression with species
included (\ref{fig:linear-example}).

\begin{Schunk}
\begin{figure}[htbp]

{\centering \includegraphics[width=6in]{fig/linear_example}

}

\caption[Representative linear relationships for penguin flipper length (mm) and body mass (g) for Adélie (orange circles), chinstrap (blue triangles), and gentoo (green squares) penguins (A), and iris petal length (cm) and width (cm) for setosa (light gray circles), versicolor (dark gray triangles) and virginica (black squares) irises (B)]{Representative linear relationships for penguin flipper length (mm) and body mass (g) for Adélie (orange circles), chinstrap (blue triangles), and gentoo (green squares) penguins (A), and iris petal length (cm) and width (cm) for setosa (light gray circles), versicolor (dark gray triangles) and virginica (black squares) irises (B). Within-species linear model is visualized for each penguin or iris species.}\label{fig:linear-example}
\end{figure}
\end{Schunk}

@@

Simpson's Paradox is a data phenomenon in which a trend observed between
variables is reversed when data are pooled, omitting a meaningful
variable. While often taught and discussed in statistics courses,
finding a real-world and approachable example of Simpson's paradox can
be a challenge. Here, we show one (of several possible; see Figure
\ref{fig:penguins-pairs}) Simpson's Paradox examples in
\textbf{penguins}: exploring bill dimensions with and without
\emph{species} included (Figure \ref{fig:simpsons}). When penguin
\emph{species} is omitted (Figure \ref{fig:simpsons} A), bill length and
depth appear negatively correlated overall. The trend is reversed when
\emph{species} is included, revealing an obviously positive correlation
between bill length and bill depth within species (Figure
\ref{fig:simpsons} B).

\begin{Schunk}
\begin{figure}[htbp]

{\centering \includegraphics[width=6in]{fig/simpson_gg}

}

\caption[Trends for penguin bill dimensions (bill length and bill depth, millimeters) if the ‘species’ variable is excluded (A) or included (B), illustrating Simpson’s Paradox]{Trends for penguin bill dimensions (bill length and bill depth, millimeters) if the ‘species’ variable is excluded (A) or included (B), illustrating Simpson’s Paradox. Note: linear regression for bill dimensions without including species in (A) is ill-advised; the linear trendline is only included to visualize trend reversal for Simpson’s Paradox when compared to (B).}\label{fig:simpsons}
\end{figure}
\end{Schunk}

@@

A comparison of PCA with the four variables of structural size
measurements in \textbf{penguins} and \textbf{iris} (both normalized
prior to PCA) reveals highly similar results (Figure \ref{fig:pca}). For
both datasets, one species is distinct (gentoo penguins, and setosa
irises) while the other two species (chinstrap/Adélie and
versicolor/virginica) appear somewhat overlapping in the first two
principal components (Figure \ref{fig:pca} A,B). Variance explained by
each principal component (PC) is similar, particularly for PC1 and PC2:
for \textbf{penguins}, 88.15\% of total variance is captured by the
first two PCs, compared to 95.81\% for \textbf{iris}, with a similarly
large percentage of variance captured by PC1 and PC2 in each (Figure
\ref{fig:pca} C,D).

\begin{Schunk}
\begin{figure}[htbp]

{\centering \includegraphics[width=6in]{fig/pca_plots}

}

\caption[Principal component analysis biplots and scree plots for structural size measurements in penguins (A,C) and iris (B,D), revealing similarities in multivariate patterns, variable loadings, and variance explained by each component]{Principal component analysis biplots and scree plots for structural size measurements in penguins (A,C) and iris (B,D), revealing similarities in multivariate patterns, variable loadings, and variance explained by each component. For penguins, variables are flipper length (mm), body mass (g), bill length (mm) and bill depth (mm); groups are visualized by species (Adélie = orange circles, chinstrap = blue triangles, gentoo = green squares). For iris, variables are petal length (cm), petal width (cm), sepal length (cm) and sepal width (cm); groups are visualized by species (setosa = light gray circles, versicolor = dark gray triangles, virginica = black squares). Values above scree plot columns (C,D) indicate percent of total variance explained by each of the four principal components.}\label{fig:pca}
\end{figure}
\end{Schunk}

@@

K-means clustering with penguin bill dimensions and iris petal
dimensions yields largely distinct clusters each dominated by one
species (\ref{fig:kmeans}). For iris petal dimensions, k-means yields a
perfectly separated cluster (Cluster 1) containing all 50 setosa iris
observations and zero misclassified virginica or versicolor irises
(Table 2). While clustering is not perfectly distinct for any penguin
species, each species is largely contained within a single cluster, with
little overlap from the other two species. For example, considering
Adélie penguins (orange observations in Figure \ref{fig:kmeans} A): 147
(out of 151) Adélie penguins are assigned to Cluster 1, zero are
assigned to Cluster 2, and 4 are assigned to the chinstrap-dominated
Cluster 3 (Table 2). Only 5 (of 68) chinstrap penguins and 1 (of 123)
gentoo penguins are assigned to the Adélie-dominated Cluster 1 (Table
2).

\begin{Schunk}
\begin{figure}[htbp]

{\centering \includegraphics[width=6in]{fig/kmeans}

}

\caption[K-means clustering outcomes for penguin bill dimensions (A) and iris petal dimensions (B)]{K-means clustering outcomes for penguin bill dimensions (A) and iris petal dimensions (B). Numbers indicate the cluster to which an observation was assigned, revealing a high degree of separation between species for both penguins and iris.}\label{fig:kmeans}
\end{figure}
\end{Schunk}

\caption{\label{tab:unnamed-chunk-3}K-means cluster assignments by species based on penguin bill length (mm) and depth (mm), and iris petal length (cm) and width (cm).}
\centering
\begin{tabular}[t]{c|c|c|c|c|c|c|c}
\hline
\multicolumn{4}{c|}{Penguins cluster assignments} & \multicolumn{4}{c}{Iris cluster assignments} \\
\cline{1-4} \cline{5-8}
Cluster & Adélie & chinstrap & gentoo & Cluster & setosa & versicolor & virginica\\
\hline
1 & NA & 9 & 116 & 1 & NA & 48 & 4\\
\hline
2 & 4 & 54 & 6 & 2 & NA & 2 & 46\\
\hline
3 & 147 & 5 & 1 & 3 & 50 & NA & NA\\
\hline
\end{tabular}
\end{table}
